\chapter{Acknowledgements}

First and foremost, I would like to thank my supervisors Jeppe Revall Frisvad and Andreas B\ae rentzen. In particular, I would like to thank Jeppe for the support during the PhD, the deep technical discussions and a push to strive for perfection. I would like to thank Andreas for the deep and interesting discussion on how to push my work towards more and more challenging directions. I would also like to thank my managers and mentors during my internship at the real-time rendering research group in NVIDIA: Craig Kolb, Marco Salvi, Aaron Lefohn and David Luebke, for sharing some of their deep knowledge about graphics. Finally, I would like to thank Toshiya Hachisuka and its group for hosting me at Tokyo University, for the their hospitality and the interesting discussions.

I would like to thank DTU Compute for financing my scholarship and giving me the opportunity to pursue a PhD in the realm of computer graphics.

A great thank you of course goes to my colleagues, collaborators, and office mates at the section for Image Analysis and Computer Graphics. Thank you for the continuous support, the coffee calls, and the general silliness that makes everyday a fun day to come to the office. It has been a great pleasure to be part of this section, sharing thoughts and ideas, and having interesting discussion over a coffee.

Last but not least, I would like to thank my loving family and friends. Without your continuous support and help, I would not have been able to complete this endeavor. 