\chapter*{List of contributions}
\label{sec:contributionlist}
\section*{Peer rewiewed}
\begin{itemize}
\item \textbf{Alessandro Dal Corso}, Jeppe Revall Frisvad, Jesper Mosegaard, and J. Andreas Bærentzen. Interactive directional subsurface scattering and transport of emergent light. \textit{The Visual Computer}, 33(3):371–383, Mar 2017.~\cite{dalcorso17dirsss}
\item Jonathan Dyssel Stets, \textbf{Alessandro Dal Corso}, Jannik Boll Nielsen, Rasmus Ahrenkiel Lyngby, Sebastian Hoppe Nesgaard Jensen, Jakob Wilm, Mads Brix Doest, Carsten Gundlach, Eythor Runar Eiriksson, Knut Conradsen, Anders Bjorholm Dahl, Jakob Andreas Bærentzen, Jeppe Revall Frisvad, and Henrik Aanæs. Scene reassembly after multimodal digitization and pipeline evaluation using photorealistic rendering. \textit{Applied Optics}, 56(27):7679–7690, Sep 2017.~\cite{stets17}
\item \textbf{Alessandro Dal Corso}, Marco Salvi, Craig Kolb, Jeppe Revall Frisvad, Aaron Lefohn, and David Luebke. Interactive stable ray tracing. In \textit{Proceedings of High Performance Graphics}, HPG ’17, pages 1:1–1:10, New York, NY, USA, 2017. ACM. \cite{dalcorso17hpg}
\item \textbf{Alessandro Dal Corso}, Jonathan Dyssel Stets, Andrea Luongo, Jannik Boll Nielsen, Jeppe Revall Frisvad, and Henrik Aanæs. Virtual reality inspection and painting with measured brdfs. In \textit{SIGGRAPH Asia 2017 VR Showcase}, SA ’17, pages 15:1–15:2, New York, NY, USA, 2017. ACM.~\cite{dalcorso17vr}
\item \textbf{Alessandro Dal Corso}, Jeppe Revall Frisvad, Thomas Kim Kjeldsen, and Jakob Andreas Bærentzen. Interactive Appearance Prediction for Cloudy Beverages. In Reinhard Klein and Holly Rushmeier, editors, \textit{Workshop on Material Appearance Modeling}. The Eurographics Association, 2016.~\cite{dalcorsomam16}
\end{itemize}

\section*{Non included}
\begin{itemize}
\item Henrik Aanæs, Knut Conradsen, \textbf{Alessandro Dal Corso}, Anders Bjorholm Dahl, Alessio Del Bue, Mads Emil Brix Doest, Jeppe Revall Frisvad, Sebastian Hoppe Nesgaard Jensen, Jannik Boll Nielsen, Jonathan Dyssel Stets, et al. Our 3d vision datasets in the making. In CVPR Workshop: The Future of Datasets in Vision 2015, 2015.~\cite{aanaes2015our}
\item \textbf{Alessandro Dal Corso}, Mikkel Olsen, Kasper Hornbak Steenstrup, Jakob Wilm, Sebastian Jensen, Rasmus Reinhold Paulsen, Eythor Eiríksson, Jannik Boll Nielsen, Jeppe Revall Frisvad, Gudmundur Einarsson, and Hans Martin Kjer. Virtualtable: A projection augmented reality game. In \textit{SIGGRAPH Asia 2015 Posters}, SA ’15, pages 40:1–40:1, New York, NY, USA, 2015. ACM.~\cite{dalcorsosig15}
\end{itemize}

\section*{Unpublished material}
\begin{itemize}
\item \textbf{Alessandro Dal Corso, Jeppe Revall Frisvad, Thomas Kim Kjeldsen}. \textit{Derivation of standard and directional dipole quantities.} Unpublished note. Text in Appendix~\ref{sec:jensennote}.
\item \textbf{Alessandro Dal Corso, Jeppe Revall Frisvad}. \textit{On measuring BSSRDFs.} Unpublished note. Text in Appendix~\ref{sec:bssrdfnote}.
\item \textbf{Alessandro Dal Corso, Jeppe Revall Frisvad}. \textit{Point cloud method for rendering BSSRDFs.} Unpublished note. Text in Appendix~\ref{sec:pointcloudnote}.
\item \textbf{Alessandro Dal Corso}. \textit{Note on efficient color calibration}. Unpublished note. Text in Appendix~\ref{sec:colornote}.
\item \textbf{Alessandro Dal Corso}. \textit{Note on BSSRDF importance sampling from the camera, derivation from Mertens et al.}. Unpublished note. Text in Appendix~\ref{sec:mertensnote}.
\end{itemize}


